Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-05-11 intro.tex
Added intro changes from Anthony

Our hackweek model shares some similarities to those summer schools (e.g., Advanced Course on Computational Neuroscience, Okinawa Computational Neuroscience Course, Woods Hole Computational Neuroscience Summer course) that combine individual or group project work with teaching methods that transfer knowedge from experts to early-career researchers.

>>>>

Our hackweek model shares some similarities to those summer schools (e.g., Advanced Course on Computational Neuroscience, Okinawa Computational Neuroscience Course, Woods Hole Computational Neuroscience Summer course) that combine individual or group project work with teaching methods that transfer knowledge from experts to early-career researchers.
